---
title: "SQL Group Project"
author: "Group - Hosh Bash"
date: "12/15/2019"
output: 
  html_document:
    toc: true
    toc_float: true
---

# Summary

The source of dataset is American Statistical Association and Bureau of Transportation Statistics, USA. Our data is related to Airlines Statistics mostly reporting Carriers and their On-Time Performance while on-flight. The years of data includes from 2005 to 2008. In
Below, all variables included in dataset can be found. You can find source of the dataset on this [website](http://stat-computing.org/dataexpo/2009/the-data.html)

```{r,message=FALSE}

tmp=tempfile(fileext=".xlsx")

download.file("https://github.com/pjournal/mef03g-polatalemd-r/blob/master/data_fields_BDM.xlsx?raw=true",destfile=tmp,mode='wb')
raw_data=readxl::read_excel(tmp)
file.remove(tmp)

head(raw_data, 40)

``` 


# Acquiring Data

The data was downloaded from the indicated website above and unzipped. In order to have it explanatory, additional support data related to carriers, planes, airports were also provided. 

```{r,message=FALSE}
flight_2008 <- read.csv("C:/Users/Berk Cakar/Desktop/2008.csv")
flight_2007 <- read.csv("C:/Users/Berk Cakar/Desktop/2007.csv")
flight_2006 <- read.csv("C:/Users/Berk Cakar/Desktop/2006.csv")
flight_2005 <- read.csv("C:/Users/Berk Cakar/Desktop/2005.csv")
planes <- read.csv("C:/Users/Berk Cakar/Desktop/planes.csv")
airports <- read.csv("C:/Users/Berk Cakar/Desktop/airports.csv")
carriers <- read.csv("C:/Users/Berk Cakar/Desktop/carriers.csv")

``` 


# Processing Data

Downloaded data was integrated by  read_csv command of R itself.  Since data has been clean and very tidy, no additional cleaning process was executed - (the discovery phase took time to find such data). 

# Libraries utilized 

Five different open source libraries of R environment were used for the analyses and execution of big data management to proceed

```{r,results='hide',message=FALSE}
library(tidyverse)
library(dplyr)
library(sqldf)
library(knitr)
library(kableExtra)
```

#Analysing the Big Data

Since data size is too big (size of 600MegaByte), several years were selected specifically to obtain insights.

## Insights

### 1. Top 10 Carriers by Total Air Time in 2008

This analysis helps to observe the Airline companies that have the highest time during flights in 2008. 

```{r,message=FALSE}
analyse_1 <- sqldf("WITH airtime AS (
SELECT UniqueCarrier, sum(AirTime) as TotalAirTime 
FROM flight_2008 
GROUP BY UniqueCarrier)
SELECT case when b.Description like 'US Airways Inc. %' then 'US Airways Inc.' else b.Description end as Carrier, TotalAirTime 
FROM airtime a
LEFT JOIN carriers b on a.UniqueCarrier = b.Code
ORDER BY TotalAirTime DESC
LIMIT 10")

kable(analyse_1) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

``` 

### 2. Top 10 Airplane Models by Total Air Time in 2008

Understanding different planes total flight time in 2008.


```{r,message=FALSE}
analyse_2 <- sqldf("WITH airtime AS(
SELECT TailNum, sum(airtime) as total_air_time
from flight_2008
GROUP BY TailNum
)
SELECT (b.manufacturer||' '||b.model) as PlaneModel, sum(a.total_air_time) as TotalAirTime 
FROM airtime a
LEFT JOIN planes b on a.TailNum = b.tailnum
WHERE b.manufacturer !=''
and b.model !=''
GROUP BY PlaneModel
ORDER BY TotalAirTime DESC
LIMIT 10")

kable(analyse_2) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

``` 

### 3. The Most Popular 20 Routes of 2008
This is quite critical to see which cities are heaviest on incoming and outgoing transfer among them. SF-LA is the most popular route following with LA-SF in 2008.

```{r,message=FALSE}
analyse_3 <- sqldf("WITH routes AS(
SELECT origin, Dest, count(*) as num_flights
FROM flight_2008 a
GROUP BY Origin, Dest
ORDER BY num_flights DESC
),
cities AS(
SELECT a.Origin, a.Dest, a.num_flights, b.city as origin_city, c.city as destination_city
FROM routes a
LEFT JOIN airports b on a.Origin=b.iata
LEFT JOIN airports c on a.Dest=c.iata)
SELECT (origin_city||'->'||destination_city) as FlightRoute, num_flights as NumberOfFlights
FROM cities
LIMIT 20")

kable(analyse_3) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

``` 

### 4. Weekly Number of Flights in 2008
This analysis is required to see which weeks are on peak and which ones are on low demand.

```{r,message=FALSE}
analyse_4 <- sqldf("WITH weekly_flights AS(
SELECT case when month = 1 then 'January'
when month = 2 then 'February' when month = 3 then 'March'
when month = 4 then 'April' when month = 5 then 'May'
when month = 6 then 'June' when month = 7 then 'July'
when month = 8 then 'August' when month = 9 then 'September'
when month = 10 then 'October' when month = 11 then 'November'
when month = 12 then 'December' else 0 end as month,
case when DayofMonth in (1,2,3,4,5,6,7) then 1
when DayofMonth in (8,9,10,11,12,13,14) then 2
when DayofMonth in (15,16,17,18,19,20,21) then 3
else 4 end as WeekofMonth, count(*) as num_flights
From flight_2008
GROUP BY month, WeekofMonth)
SELECT (WeekofMonth||'. Week of '||month) as WeekOfFlight,num_flights as NumberOfFlights
FROM weekly_flights
ORDER BY NumberOfFlights desc")

ggplot(data = analyse_4, aes(x = reorder(WeekOfFlight, -NumberOfFlights), y = NumberOfFlights)) + geom_bar(stat = "identity") + 
  labs(x = "", y = "", title = "Weekly Number of Flights in 2008") + 
  theme_bw() + theme( axis.text.x = element_text(angle = 90,vjust = 0.49, hjust = 0.49, size = 5)) +
  scale_y_continuous(labels = scales::comma) + theme(line=element_blank())

``` 

### 5. Top 5 Airports with the Highest Number of Delays Due To Weather Conditions
Delay is one of the most important topic in airline industry. This insight is to observe which airports have the highest incident numbers to showcase the issues elated to weather conditions.

```{r,message=FALSE}
analyse_5 <- sqldf("
SELECT fl.Origin as AirportCode,ai.airport as Airport,ai.city as City,count(*) as NumberOfDelays
FROM flight_2008 fl
  INNER JOIN airports ai ON fl.Origin = ai.iata
WHERE fl.CarrierDelay > 30
GROUP BY fl.Origin,ai.airport,ai.city,ai.country
ORDER BY NumberOfDelays DESC
LIMIT 5
      ")

kable(analyse_5) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

``` 

### 6.  Delay Trend of Worst Airline Companies between 2005-2008
Worst airline company definiton: number of delays occured higher than 30 minutes
The insight helps to show the improvement areas and development needs for each airlines with four years trend data

```{r,message=FALSE}
worst_carriers <- sqldf("
SELECT fl.UniqueCarrier,ca.Description,count(*) as total_number_of_delays,fl.Year
FROM flight_2008 fl
  INNER JOIN carriers ca ON fl.UniqueCarrier = ca.Code
WHERE fl.CarrierDelay > 30
GROUP BY fl.UniqueCarrier,ca.Description,fl.Year
ORDER BY count(*) DESC
LIMIT 5
      ")

x <- c("flight_2005","flight_2006","flight_2007","flight_2008")
y <- vector(mode = "list", length = 4)

for (i in 1:4){
  y[[i]] <- sqldf(sprintf("
    SELECT fl.UniqueCarrier,ca.Description,count(*) as total_number_of_delays,fl.Year
    FROM %s fl
      INNER JOIN carriers ca ON fl.UniqueCarrier = ca.Code
    WHERE fl.CarrierDelay > 30
    AND fl.UniqueCarrier IN (SELECT UniqueCarrier
                              FROM worst_carriers)
    GROUP BY fl.UniqueCarrier,ca.Description,fl.Year
    ORDER BY count(*) DESC
    LIMIT 5  
  ",x[i]))
}


four_year_total_delays <- bind_rows(y)

four_year_total_delays %>%
  ggplot(aes(x = Year,y=total_number_of_delays,color = Description))+
  geom_line()

``` 



